Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-19 Supplemental Material B - Coding Protocol/margins/FactSheet.tex
coding protocol filled

\input{Supplemental Material A - Coding Protocol/margins/empNums}

@@

% Top Matter
\NFtitle\\
\NFrule
\NFtext{\textbf{Dataset} Empirical Acculturation Literature}\\
\NFtext{\textbf{Instances Per Dataset} \nEmp\ empirical studies from \nAllEmp\ unique manuscripts}\\

% Motivation Section
\NFRULE
\NFline{Motivation}\\
\NFrule
\NFelement{Original Authors}{}{Kreienkamp, Bringmann, Engler, de Jonge, Epstude}\\
\NFelement{Original Use Case}{}{collection of empirical works}\\
\NFelement{Original Funding}{}{None}\\

@@

% Composition Section
\NFRule
\NFline{Composition}\\
\NFrule
\NFelement{Sample or Complete}{}{Sample}\\
\NFelement{Missing Data}{}{\percEmpInaccess\% not accessible \\\hfill(\percEmpItemInaccess\% items \& \percEmpThesisInaccess\% theses not accessible)\\\hfill+ see Screening}\\
\NFelement{Sensitive Information }{}{author information}\\
%\NFelement{Additional Field}{}{Info}\\

% Collection Process Section
\NFRule
\NFline{Collection}\\
\NFrule
\NFelement{Sampling Strategy}{}{systematic review (see search strategy)}\\
\NFelement{Ethical Review}{}{not applicable}\\
\NFelement{Author Consent}{}{not applicable}\\
%\NFelement{Additional Field}{}{Info}\\

@@

% Uses / Distribution Section
\NFRule
\NFline{Uses and Distribution}\\
\NFrule
\NFelement{Notable Uses}{}{this systematic review}\\
\NFelement{Other Uses}{}{openly accessible for further analysis}\\
\NFelement{Distribution}{}{available on OSF and GitHub}\\
%\NFelement{Replicate Distribution}{}{Info}\\
%\NFelement{Additional Field}{}{Info}\\

@@

\NFRULE
\NFline{Types of publications \hfill\% of manuscripts*}\\
\NFrule
\NFelement{journal articles}{\nJournal\,manuscripts}{\percJournal\%}\\
\NFrule
\NFelement{theses}{\nThesis\,manuscripts}{\percThesis\%}\\
\NFrule
%\NFelement{book chapters}{6\,manuscripts}{1.1\%}\\
%\NFrule
%\NFelement{Another}{count}{XX\%}\\
%\NFrule
\NFentry{book chapters \percChapter\%} \\
%\NFentry*{framework 2.9\%}\\
%\NFentry{Red 1.5\%}\\
%\NFrule
%\NFtext{As identified by the author(s) of the theoretical manuscripts (also see `FrameworkTheoryModel' code).}\\
\NFrule
\NFtext{* Based on final dataset after screening.}
\end{tabular}}

>>>>

@@

% Top Matter
\NFtitle\\
\NFrule
\NFtext{\textbf{Dataset} Acculturation over Time Studies}\\
\NFtext{\textbf{Instances Per Dataset} \hl{X,XXX} free text responses in \hl{XX} topics}\\

% Motivation Section
\NFRULE
\NFline{Motivation}\\
\NFrule
\NFelement{Original Authors}{}{Kreienkamp, Agostini, Bringmann, de Jonge, Epstude}\\
\NFelement{Original Use Case}{}{cultural adaptation in daily interactions}\\
\NFelement{Original Funding}{}{No specific}\\

@@

% Composition Section
\NFRule
\NFline{Composition}\\
\NFrule
\NFelement{Sample or Complete}{}{Complete}\\
\NFelement{Missing Data}{}{\hl{X.X}\% excluded}\\
\NFelement{Sensitive Information }{}{free text responses}\\
%\NFelement{Additional Field}{}{Info}\\

% Collection Process Section
\NFRule
\NFline{Collection}\\
\NFrule
\NFelement{Sampling Strategy}{}{experience sampling method (ESM)}\\
\NFelement{Ethical Review}{}{University masked for Peer review}\\
\NFelement{Author Consent}{}{not applicable}\\
%\NFelement{Additional Field}{}{Info}\\

@@

% Uses / Distribution Section
\NFRule
\NFline{Uses and Distribution}\\
\NFrule
\NFelement{Notable Uses}{}{non published data}\\
\NFelement{Other Uses}{}{partially open for further analysis}\\
\NFelement{Distribution}{}{available on OSF and GitHub}\\
%\NFelement{Replicate Distribution}{}{Info}\\
%\NFelement{Additional Field}{}{Info}\\

@@

\NFRULE
\NFline{Sample Sizes per study \hfill\% of total*}\\
\NFrule
\NFelement{Study 1}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
\NFrule
\NFelement{Study 2}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
\NFrule
\NFelement{Study 3}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
% \NFrule
%\NFelement{Another}{count}{XX\%}\\
%\NFrule
% \NFentry{we focus on outgroup interactions for this analysis} \\
%\NFentry*{framework 2.9\%}\\
%\NFentry{Red 1.5\%}\\
\NFrule
\NFtext{For the analysis using this coding we focused on outgroup interactions only (also see `introduction').}\\
\NFrule
\NFtext{* based on outgroup interaction responses.}
\end{tabular}}
